### 2024-05-06 Paper/paper.tex
Updates from Overleaf

    \begin{equation}
    \label{eq:forprofit}
    y_{ht} = \beta (\text{for-profit}_h \times \text{post programs}_t) + \gamma_{h} + \delta_t + \epsilon_{ht}
    \end{equation}

@@

    \begin{equation}
    \label{eq:clinical}
    y_{ht} = \beta (\text{no MD exec}_h \times \text{post programs}_t) + \gamma_{h} + \delta_t + \epsilon_{ht}
    \end{equation}

@@

    \begin{equation}
    \label{eq:decomp}
    y_{ht} = \beta (\text{never/no 2012 exec}_h \times \text{post programs}_t) + \gamma_{h} + \delta_t + \epsilon_{ht}
    \end{equation}

@@

@@

@@

\section{Full Sample Regression Results}\label{app:fullsample}

@@

>>>>

    \begin{equation}
    \label{eq:forprofit}
    y_{ht} = \beta (\text{For-Profit}_h \times \text{Post Programs}_t) + \gamma_{h} + \delta_t + \epsilon_{ht}
    \end{equation}

@@

    \begin{equation}
    \label{eq:clinical}
    y_{ht} = \beta (\text{No MD Exec}_h \times \text{Post Programs}_t) + \gamma_{h} + \delta_t + \epsilon_{ht}
    \end{equation}

@@

    \begin{equation}
    \label{eq:decomp}
    y_{ht} = \beta (\text{Never/No 2012 Exec}_h \times \text{Post Programs}_t) + \gamma_{h} + \delta_t + \epsilon_{ht}
    \end{equation}

@@

     \begin{figure}
         \centering
         \caption{Readmission Results}
         \includegraphics[width=\textwidth]{Objects/read_synth_plot.pdf}
         \label{fig:read_synth_plot}
     \end{figure}

@@

      \begin{figure}
         \centering
         \caption{Mortality Results}
         \includegraphics[width=\textwidth]{Objects/mort_synth_plot.pdf}
         \label{fig:read_synth_plot}
     \end{figure}

@@

\section{Full Sample Regression and Event Study Results}\label{app:fullsample}

@@

\section{Synthetic Diff-in-Diff Result Tables}
